---
title: "Linear Regression Analysis of Business Data of Taco Restaurants"
output: "html_document"
---

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(MASS)
library(stats)
library(leaps)
library(missMethods)
library(regclass)
```

```{r}
business = read.csv("data/business.csv")
```


```{r}
business
```

`


```{r}
taco = read.csv("data/business_xy.csv")
```


```{r}
for_plot <- taco[,150:161] ##only choose attributes and time// we only select those retaurants with "taco, restaurants" in the name of the business
```



We would like to contain no more than 5 variables in our regression model for the simplicity of explanation. First we use all subsets regression to select the best model with no more than 5 indicators.  
```{r}
impute_plot <- impute_mode(for_plot, type = "columnwise", convert_tibble = TRUE)
step.model <- regsubsets(stars~., data = impute_plot, nvmax=5, method = "seqrep")
summary(step.model)
```

```{r}
res.sum <- summary(step.model)
data.frame(
  Adj.R2 = res.sum$adjr2,
  CP =res.sum$cp,
  BIC = res.sum$bic
)
```
From the value of these three metrics, it shows that regression model with 5 indicators Outdoor Seating, Bike Parking, Restaurants TakeOut, Restaurants Delivery , and Weekends is the 'best' model


```{r}
model1 <-lm(stars ~ X.ATTR..BikeParking+X.TIME..Weekends+X.ATTR..RestaurantsTakeOut+X.ATTR..RestaurantsDelivery+X.ATTR..OutdoorSeating , data = for_plot)
summary(model1)
```

Since one-hot encoding will make the linear regression model suffer multicolinearity, we use variance inflation factor to check. The value of VIF is less than 5 as well as $\frac{1}{1-R^2} = 1.883239$, which means our model does not suffer severe multicolineairty and can provide statistical significant explanations.

```{r}
VIF(model1)
```

```{r}
1/(1-0.469)
```


```{r}
na.omit(for_plot[c("X.ATTR..OutdoorSeating","stars")])%>%
  group_by(X.ATTR..OutdoorSeating)%>%
  summarise(good = sum(stars>=3)/n())
na.omit(for_plot[c("X.ATTR..BikeParking","stars")])%>%
  group_by(X.ATTR..BikeParking)%>%
  summarise(good = sum(stars>=3)/n())
na.omit(for_plot[c("X.TIME..Weekends","stars")])%>%
  group_by(X.TIME..Weekends)%>%
  summarise(good = sum(stars>=3)/n())
na.omit(for_plot[c("X.ATTR..RestaurantsTakeOut","stars")])%>%
  group_by(X.ATTR..RestaurantsTakeOut)%>%
  summarise(good = sum(stars>=3)/n())
na.omit(for_plot[c("X.ATTR..RestaurantsDelivery","stars")])%>%
  group_by(X.ATTR..RestaurantsDelivery)%>%
  summarise(good = sum(stars>=3)/n())
```
















